Metropolitan Statistical Area Evaluation

### 2022-11-01 src/demo_data_wrangling.Rmd
added missing employment data and normalized values
median rent for MSAs

yoy <- (employment_data_jan_2022 - employment_data_jan_2021)/ employment_data_jan_2022 *100

@@

>>>>

yoy <- (employment_data_jan_2022 - employment_data_jan_2021)/ employment_data_jan_2021 *100

@@

2021 Median Rent from https://www.huduser.gov/portal/datasets/50per.html#2021

```{r}
# median rents from hud
MSA_median_rent2021_data <- read_csv(here("data", "raw", "2021MSA_medianrent.csv")) %>% 
  separate(col = cbsasub21,
           into = c("metro", "cbsa"),
           sep = -5) %>% 
  mutate(cbsa = as.double(cbsa)) %>% 
  select(cbsa, rent50_0, rent50_1, rent50_2, rent50_3, rent50_4) %>% 
  right_join(potential_MSAs) 
```
